---
title: "LOBtools: Further Screen and Visualize LOBSTAHS lipid annotations."
output: html_notebook
---

This document serves as a vignette on the new functionality presented in LOBtools. We use the XYZ data set too illustrate the new tools available for lipid screening and data visualization in this package.

Much like previous LOBSTAHS package vignettes, this will not serve as a comprehensive overview of the XCMS and CAMERA packages, as many great tutorials and vignettes already exist for these packages. However, we will provide the code used in pre-processing our samples for screening by LOBSTAHS and LOBtools which can be found here (URL).


```{r}

```

Load Data
```{r}
#read mzXML files into an OnDiskMSnExp object
mzXMLfiles <- list.files("C:/Users/henryholm/Desktop/JenkinAE1812ctd/", recursive = TRUE, full.names = TRUE)
rawSpec <- MSnbase::readMSData(mzXMLfiles, centroided=TRUE, mode="onDisk")

```

Find MS2
```{r}
peaklist <- getLOBpeaklist(LOBset)
LOBtools::LOB_plotMS2(XCMSnExp = rawSpec,peakdata = subset(peaklist,species == "SQDG"))
```


RtF Screen
```{r}
Hummel <- read.csv(file = "C:/Users/henryholm/Downloads/Hummel RtF Master Database - rtf_data.csv")

LOBset <- ptH2O2lipids$LOBSet

LOBset_rtf <- LOBtools::LOB_RTFsort(peakdata = LOBset,Hummel)

LOBtools::LOB_plotMS2()

```

